### 2018-01-09 ident/docs/ident_manuscript.tex
figure caption update and methods update

\subsection{Identifiability of parameters in a kinetic model of gluconeogenesis:}\label{sec:example}
Here, we demonstrate the use of our computer algebra-based methodology to establish practical identifiability of parameters for flux $v_2$ in the small model of gluconeogenesis described in Section \ref{sec:small-model}. We choose flux $v_2$, expressed using Michaelis-Menten kinetics for this demonstration. $v_2$ has two parameters, $V_2^{max}$ and $K_2^{pep}$ that need to be identifiable so that they can be estimated from experimental data. Here, we assume that data (for the concentrations and fluxes) from at least two different sets of experiments is available. We label the available concentrations as ${pep}^1$ and ${pep}^2$, and the fluxes as ${v_2}^1$ and ${v_2}^2$ respectively, from each experiment. Accordingly, the nonlinear algebraic equations shown in Equation (\ref{eq:nonlineq}) can be formulated for flux $v_2$ as follows:
\begin{subequations}\label{eq:nonlin-flux2}
	\begin{align}
	{v_2}^1 = V_{2}^{max}\frac{pep^1}{pep^1+K_{2}^{pep}}\\
	{v_2}^2 = V_{2}^{max}\frac{pep^2}{pep^2+K_{2}^{pep}}
	\end{align}
\end{subequations}
Solving this simultaneous system of equations using Mathematica (Wolfram Research, USA), a computer algebra system, we get two nonlinear algebraic equations in the parameters $V_2^{max}$ and $K_2^{pep}$ based on the form shown earlier in Equation (\ref{eq:theta-eq}).
\begin{subequations}\label{eq:v2_par}
	\begin{align}		
	V_2^{max} = \frac{v_2^1v_2^2(pep^1-pep^2)}{v_2^2pep^1-v_2^1pep^2}\\
	K_2^{pep} = \frac{pep^1(v_2^1pep^2-v_2^2pep^2)}{v_2^2pep^1-v_2^1pep^2}
	\end{align}
\end{subequations}
In Equation (\ref{eq:v2_par}), the denominator of the right hand side expression is used to test the identifiability of parameters $V_2^{max}$ (Equation \ref{eq:v2_par}a) and $K_2^{pep}$ (Equation \ref{eq:v2_par}b) for different available experimental data set combinations. Since the enzyme binding constant ($K_2^{pep}$) and maximum reaction rate ($V_2^{max}$) cannot be negative, we can further reduce the criteria for identifiability for both these parameters by saying that the evaluated expressions should be non-negative.

\section{Results:}
\begin{figure}[!tbhp]
	\centering{\includegraphics[width=.6\textwidth,height=.6\textheight,keepaspectratio]{C:/Users/shyam/Documents/Courses/CHE1125Project/Results/ident/figure3/ident_analysis}}
	\caption{to be filled in}\label{fig:figure1}
\end{figure}

>>>>

\subsection{Identifiability of parameters in a kinetic model of gluconeogenesis:}\label{sec:example}
Here, we demonstrate the use of our computer algebra-based methodology to establish practical identifiability of parameters for fluxes $v_1$, $v_2$ and $v_3$ in the small model of gluconeogenesis described in Section \ref{sec:small-model}.

For flux $v_1$
We choose flux $v_2$, expressed using Michaelis-Menten kinetics for this demonstration. $v_2$ has two parameters, $V_2^{max}$ and $K_2^{pep}$ that need to be identifiable so that they can be estimated from experimental data. Here, we assume that data (for the concentrations and fluxes) from at least two different sets of experiments is available. We label the available concentrations as ${pep}^1$ and ${pep}^2$, and the fluxes as ${v_2}^1$ and ${v_2}^2$ respectively, from each experiment. Accordingly, the nonlinear algebraic equations shown in Equation (\ref{eq:nonlineq}) can be formulated for flux $v_2$ as follows:
\begin{subequations}\label{eq:nonlin-flux2}
	\begin{align}
	{v_2}^1 = V_{2}^{max}\frac{pep^1}{pep^1+K_{2}^{pep}}\\
	{v_2}^2 = V_{2}^{max}\frac{pep^2}{pep^2+K_{2}^{pep}}
	\end{align}
\end{subequations}
Solving this simultaneous system of equations using Mathematica (Wolfram Research, USA), a computer algebra system, we get two nonlinear algebraic equations in the parameters $V_2^{max}$ and $K_2^{pep}$ based on the form shown earlier in Equation (\ref{eq:theta-eq}).
\begin{subequations}\label{eq:v2_par}
	\begin{align}		
	V_2^{max} = \frac{v_2^1v_2^2(pep^1-pep^2)}{v_2^2pep^1-v_2^1pep^2}\\
	K_2^{pep} = \frac{pep^1(v_2^1pep^2-v_2^2pep^2)}{v_2^2pep^1-v_2^1pep^2}
	\end{align}
\end{subequations}
In Equation (\ref{eq:v2_par}), the denominator of the right hand side expression is used to test the identifiability of parameters $V_2^{max}$ (Equation \ref{eq:v2_par}a) and $K_2^{pep}$ (Equation \ref{eq:v2_par}b) for different available experimental data set combinations. Since the enzyme binding constant ($K_2^{pep}$) and maximum reaction rate ($V_2^{max}$) cannot be negative, we can further reduce the criteria for identifiability for both these parameters by saying that the evaluated expressions should be non-negative.

We found that the complexity of the MWC kinetic rate law formulation precluded its use to determine closed form expressions for the parameters in $v_3$ in Mathematica. Hence, we modeled the allosterically activated flux $v_3$ using the convenience kinetic rate law formulation (reference for convenience kinetics). The corresponding expression obtained for $v_3$ is given below (Equation).

Using this expression for our identifiability analysis, we found that each of the parameters $V_3^{max}$, $K_3^{fdp}$ and $K_3^{pep}$ have two different close form expressions owing to the presence of a square root term in their solutions. These distinct expressions are denoted by (1) and (2) following the parameter names throughout the rest of the document.

\section{Results:}
\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1\textwidth,height=.8\textheight,keepaspectratio]{C:/Users/shyam/Documents/Courses/CHE1125Project/Results/ident/figure1/noise_no_noise_kotte_ident_jan01}}
	\caption{The number of data sets, made from a combination of 18 different in silico experiments that can practically identify each parameter in fluxes a) $v_1$, b) $v_2$ and c) $v_3$ when there is no noise in the input experimental data. In the presence of additive noise in the flux and concentration data used for identifiability, the number of data sets practically identifying parameters in fluxes d)$v_1$, e)$v_2$ and f)$v_3$ are shown. 25 samples of additive noise $\epsilon ~ N(0, 0.05)$ were used to generate noisy data for figures in the right hand side panel.}\label{fig:figure1}
\end{figure}
